Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-23 paper/abstraction/paper.tex
stuff

The intended policy for this network is:
$(1)$ complete internal connectivity, \IE, all routers should be able to reach each other;
$(2)$ services in Pods[1--2] should be accessible from outside;
$(3)$ prefixes for global service should be aggregated into a covering prefix PG when announced outside;
$(4)$ services in Pods[3--4] should not be externally accessible;
$(5)$ traffic paths should be valley-free, \IE, not go down then back up.
$(6)$ prefer neighbor N1 over N2, \IE, when both neighbors announce a prefix, send traffic through N1;
$(7)$ routers should not transit traffic between N1 and N2; and
$(8)$ no loss in connectivity after any single-link failure.

@@

For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ say that, within any pod P, the number of outgoing edges from a node in the $TG$ role to a node in the $AG$ role equals the number of nodes in the $AG$ role. Similarly, the number of outgoing edges from a node in the $AG$ role to a node in the $TG$ role equals the number of nodes in the $TG$ role. These constraints capture the fact that, within any pod, the global aggregators and ToRs are in a full mesh. Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure that, within pods P and Q, the $AG$ and $TG$ roles have the same number of routers, which is less than or equal to the number of routers in the spine role $S$.
%
The constraint $e3 \geq 2$ says that, in each pod, each aggregator node has at least 2 outgoing edges to nodes in the spine role. Symmetrically, the constraint $e4 \geq 1$ says that, for each pod P, each node in the spine role has at least one outgoing edge to a node in the $AG$ role. Similar constraints appear for the local aggregator role. The constraint $2 \leq S \leq 4$ makes explicit the possibility for growth, for example, by growing the network from Figure~\ref{fig:example} to Figure~\ref{fig:example2}. In general, we need not bound the number of spine routers to admit more concrete topologies, potentially at the expense of analysis precision. We also include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$~simply to show that constraints do not have to be in the form of inequalities. Operators can use logical formulas from any theory supported by modern SMT solvers.

@@

Next we can capture constraint (4) that traffic for local prefixes must stay within in the data center:
%
\begin{code}
\Define Local =
    \$LP \Path \Always(\In)
\end{code}
\noindent%
%
The Local policy adds the $\CD{\Always(\In)}$ constraint for each local prefix described by the template variable $\CD{\$LP}$. This constraint ensures that traffic follows a path that matches an internal role (\IE, in the data center) at each hop of the path.
%
The constraint to prevent ``valleys" (5) is written as:
%
\begin{code}
\Define NoValley =
    \True \Path \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
\end{code}
\noindent%
%
This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each level in the data center.
%
Constraint (7) to prevent transit traffic between neighbors is expressed as:
%
\begin{code}
\Define Peer = \{N1,N2\}
\Define NoTransit =
    \True \Path !(\Enter(Peer) & \Exit(Peer))
\end{code}
\noindent%
%
We define a $\CD{Peer}$ as $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters and exits the data center through a peer.

@@

For each regular path constraint $r_i$ from $r_1 ~\Prefer~ ... ~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$. A DFA for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ is the set of topology locations (\IE, routers or roles), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
The PG for a graph $G=(V,E)$ is a tuple ($G'$, $start$, \Pref) where $G' = (V',E')$ has
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon V' \times V'$,
a unique starting vertex $start$,
and a ranking function $\Pref \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.

The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$.
%
We add edges from the $\mathit{start}$ node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
%
The ranking function $\Pref(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $\Pref(m) = \set{i~\vert~q_{m_i} \in F_i}$.
%
Finally, we write $\Topo{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$. For the remainder of the paper, we use the term location to refer to both a router in the case of a concrete topology/PG, or a role in the case of an abstract topology/PG.

>>>>

The intended policy for this network is:
$(1)$ complete internal connectivity, \IE, all routers should be able to reach each other;
$(2)$ services in Pods[1--2] should be accessible from outside;
$(3)$ prefixes for global service should be aggregated into a covering prefix PG when announced outside;
$(4)$ services in Pods[3--4] should not be externally accessible;
$(5)$ traffic paths should be valley-free (\EG, a path through S1 should
not go down through Ai and then back up through S2, for instance, 
creating an up-down-up path);
$(6)$ prefer neighbor N1 over N2, \IE, when both neighbors announce a prefix, send traffic through N1;
$(7)$ routers should not transit traffic between N1 and N2; and
$(8)$ no loss in connectivity after any single-link failure.

@@

For example, in Figure~\ref{fig:example3}, the first constraint ($e1 = AG$) 
%and
states that, within any pod P, the number of outgoing edges from a node in the 
$TG$ role (\IE, $e1$) to a node in the $AG$ role equals the number of nodes in the 
$AG$ role. Similarly, the constraint ($e2 = TG$) states that the number of 
outgoing edges from a node in the $AG$ role (\IE, $e2$) to a node in the $TG$ role 
equals the number of nodes in the $TG$ role. Together these constraints capture 
the fact that, within any pod, the global aggregators and ToRs are in 
a full mesh. Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure 
that, within pods P and Q, the $AG$ and $AL$ roles \dpw{This originally said $AG$ and $TG$ but I changed it.} have the same number of 
routers, which is less than or equal to the number of routers in the spine 
role $S$.
%
The constraint $e3 \geq 2$ says that, in each pod, each aggregator node has at least 2 outgoing edges to nodes in the spine role. Symmetrically, the constraint $e4 \geq 1$ says that, for each pod P, each node in the spine role has at least one outgoing edge to a node in the $AG$ role. Similar constraints appear for the local aggregator role. The constraint $2 \leq S \leq 4$ makes explicit the possibility for growth, for example, by growing the network from Figure~\ref{fig:example} to Figure~\ref{fig:example2}. In general, we need not bound the number of spine routers to admit more concrete topologies, potentially at the expense of analysis precision. We also include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$~simply to show that constraints do not have to be in the form of inequalities. Operators can use logical formulas from any theory supported by modern SMT solvers.

@@

Next we can capture constraint (4) that traffic for local prefixes must stay within in the data center:
%
\begin{code}
\Define Local =
    \$LP \Path \Always(\In)
\end{code}
\noindent%
%
The \CD{Local} policy adds the $\CD{\Always(\In)}$ constraint for each local prefix described by the template variable $\CD{\$LP}$. This constraint ensures that traffic follows a path that matches an internal role (\IE, in the data center) at each hop of the path.
%
The constraint to prevent ``valleys" (5) is written as:
%
\begin{code}
\Define NoValley =
    \True \Path \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
\end{code}
\noindent%
%
This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each level in the data center.
%
Constraint (7) to prevent transit traffic between neighbors is expressed as:
%
\begin{code}
\Define Peer = \{N1,N2\}
\Define NoTransit =
    \True \Path !(\Enter(Peer) & \Exit(Peer))
\end{code}
\noindent%
%
We define a $\CD{Peer}$ as $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters and exits the data center through a peer.

@@

For each regular path constraint $r_i$ from $r_1 ~\Prefer~ ... ~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$. A DFA for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ is the set of topology locations (\IE, routers or roles), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
The PG for a graph (\IE, a topology) $G=(V,E)$ is a tuple ($G'$, $start$, \Pref) where $G' = (V',E')$ has
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon V' \times V'$,
a unique starting vertex $start$,
and a ranking function $\Pref \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.

The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$.
%
We add edges from the $\mathit{start}$ node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
%
The ranking function $\Pref(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $\Pref(m) = \set{i~\vert~q_{m_i} \in F_i}$.
%
Finally, we write $\Topo{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$. For the remainder of the paper, we use the term \emph{location} to refer to a router in the case of a concrete topology/PG, or a role in the case of an abstract topology/PG.
